---
title: "hw_4"
author: "Danielle Sclafani"
date: "5/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```
## Loading in the Data
```{r}
damages <- read_csv(here("data", "damages.csv")) %>% 
  clean_names()
warming <- read_csv(here("data", "warming.csv")) %>% 
  clean_names()
```

```{r}

ggplot(data = damages, aes(x = warming, y = damages)) + geom_point()
```

## Finding the Quadratic Formula
```{r}
#creating new variable of x^2, which is warming^2
damages$warming2 <- damages$warming^2
damages_model <- lm(damages ~ warming + warming2, data = damages)
summary(damages_model)
```

# Question #1

Formula => Damages = 1.959x10^13 (Warming^2) - 3.019X10^12(Warming), Warming = degrees Celsius increase

```{r}

warmingValues <- seq(0, 10, 0.00001)
damagesPredict <- predict(damages_model, list(warming = warmingValues, warming2=warmingValues^2))

#Original Scatterplot
plot(damages$warming, damages$damages, pch = 25) + lines(warmingValues, damagesPredict, col = "blue")

```

# Question 2

### Question 2 Part 1: Damages with the baseline temperature
```{r, fig.cap= "Figure 2.0 Damages without a pulse"}
damages_baseline <- predict(damages_model, list(warming = warming$warming_baseline, warming2=warming$warming_baseline^2))

#Original Scatterplot

plot(x = warming$year, damages_baseline)

```

### Question 2 Part 2: Damages with pulse
```{r, fig.cap= "Figure 3.0 Damages with a pulse"}
damages_pulse <- predict(damages_model, list(warming = warming$warming_pulse, warming2=warming$warming_pulse^2))

plot(damages_pulse, x = warming$year)
```
### Question 2, Part 3: Differences in Damages over time that arise form the pulse
```{r}
# differences in the warming

warming$diff <- warming$warming_pulse - warming$warming_baseline
damages_diff <- predict(damages_model, list(warming = warming$diff, warming2=warming$diff^2))

plot(damages_diff, x = warming$year)
```


### Question 2, part 4: The difference in damages over time from the pulse per ton of CO2 

```{r}
#need to convert billion tons to tons. So going to divide degrees by a billion

warming$diffton <- warming$diff/1000000000
damages_diffton <- predict(damages_model, list(warming = warming$diffton, warming2=warming$diffton^2))

plot(damages_diffton, x = warming$year)

```


# Question 3

```{r}

#choosing a date: 2070, in 50 years
warming_50 <- warming %>% 
  filter(x1 == 50)

#we plug in this temperature from 2070 to the damages function. We will use the warming_baseline temperature.
damages_50 <- predict(damages_model, list(warming = warming_50$warming_baseline, warming2=warming_50$warming_baseline^2))
damages_50 #this is the total cost of damages in 2070
```


```{r}

#making a sequence of the discount rates
discount_rates <- seq(0, 5, 0.25)

#Calculating the SCC: using the present value formula, we know that B= damages_50, and that B/r = Present Value.

present_value_50 <- damages_50/discount_rates
present_value_50

#need to get ramsey point on here
plot(present_value_50, x = discount_rates)


```

# Question 4: Using the Ramsey Rule
```{r}
r = 0.001 + 2*0.01
r

scc_ramsey <- damages_50/r
scc_ramsey

```

```{r}
plot(x = r, y = scc_ramsey, col = "blue")
```

```{r}
# putting graph into a ggplot so we can add the ramsey rule point
data_4_present_value <- as.data.frame(damages_50/discount_rates)
data_4_discount_rates <- as.data.frame(discount_rates)

ggplot(data = data_4_present_value, aes(y=data_4_present_value$`damages_50/discount_rates`, x=data_4_discount_rates$discount_rates )) + geom_point() +
  geom_point(aes(x=r, y=scc_ramsey, col = "Ramsey Rule Point")) +
  theme_minimal()

```

# Question 5
## Policy A
```{r}
# Policy A
warming$warming_policyA <- warming$warming_baseline*1.5

#year 2100
warming_2100 <- warming %>%  filter(year == 2100)


#finding damages in 2100 under baseline
damages_2100 <- predict(damages_model, list(warming = warming_2100$warming_baseline, warming2=warming_2100$warming_baseline^2))
damages_2100

#finding damages under Policy A situation#2

damages_2100_policyA <- predict(damages_model, list(warming = warming_2100$warming_policyA, warming2=warming_2100$warming_policyA^2))
damages_2100_policyA



# finding expected net damages
#Expected damages = p1(damages1) + p2(damages2)
# p1 = 0.5, damages1 = damages@baseline, p2 = 0.5, damages2=damages@policyA

expected_damages<-0.5*damages_2100 + 0.5*damages_2100_policyA 
expected_damages # this is the cost of the expected damages under Policy A scenarios

#finding the present value of the expected damages

pv_expected_damages <- expected_damages/(1+0.02)^80
pv_expected_damages #this is the present value of the expected damages in 2100 under Policy A with a risk neutral population
```



